---
title: "Project"
output: html_document
date: "2023-08-14"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(corrplot)
library(tidyverse)
library(PerformanceAnalytics)
library("odbc")

```


#### Load Data 

```{r cars}
conn = dbConnect(odbc() ,DSN="CA***Q",database='Q***est',uid='Qpp',pwd='*',port=1433)
# Value Stocks
query <- "SELECT * FROM [QIAR_TEST].[dbo].[daily_value_stock_returns] ORDER BY pricingDate asc"
stock_returns <- dbGetQuery(conn, query)
# Close the connection
stock_returns <- stock_returns[-(1:1),]

# Growth Stocks
query2 <- "SELECT * FROM [QIAR_TEST].[dbo].[daily_growth_stock_returns] ORDER BY pricingDate asc"
growth_stock_returns <- dbGetQuery(conn,query2)
growth_stock_returns <- growth_stock_returns[-(1:1),]

#Dividend Stocks
query6 <-"select * from [QIAR_TEST].[dbo].[daily_div_stock_returns] order by pricingDate asc"
div_stock_returns <- dbGetQuery(conn,query6)
div_stock_returns <- div_stock_returns[-(1:1),]

#Financial Stocks
query8 <- "select * from [QIAR_TEST].[dbo].[daily_fin_stock_returns] order by pricingDate asc"
fin_stock_returns <- dbGetQuery(conn,query8)
fin_stock_returns <- fin_stock_returns[-(1:1),]

#Capital Stocks
query10 <- "select * from [QIAR_TEST].[dbo].[daily_cap_stock_returns] order by pricingDate asc"
cap_stock_returns <- dbGetQuery(conn,query10)
cap_stock_returns <- cap_stock_returns[-(1:1),]

#Value factor Data
query4 <- "SELECT [valueDate],[value]
  FROM [Xpressfeed].[dbo].[ciqIndexValue] where tradingItemId=2644245 and dataItemId=112099 and valueDate >= DATEADD(Month,-3,GETDATE()) order by valueDate desc"
value_returns <- dbGetQuery(conn,query4)

#Growth factor data
query3 <- "SELECT [valueDate],[value]
  FROM [Xpressfeed].[dbo].[ciqIndexValue] where tradingItemId=2644243 and dataItemId=112099 and valueDate >= DATEADD(Month,-3,GETDATE()) order by valueDate desc"
growth_returns <- dbGetQuery(conn,query3)

#S&P Index Data
query5 <- "SELECT [valueDate],[value]
  FROM [Xpressfeed].[dbo].[ciqIndexValue] where tradingItemId=2633671 and dataItemId=112099 and valueDate >= DATEADD(Month,-3,GETDATE()) order by valueDate desc"
snp_returns <- dbGetQuery(conn,query5)

#Dividend Factor data
query7 <- "SELECT [valueDate],[value]
  FROM [Xpressfeed].[dbo].[ciqIndexValue] where tradingItemId=50873350 and dataItemId=112099 and valueDate >= DATEADD(Month,-3,GETDATE()) order by valueDate desc"
div_returns <- dbGetQuery(conn,query7)

#Financial Factor Data
query9 <- "SELECT [valueDate],[value]
  FROM [Xpressfeed].[dbo].[ciqIndexValue] where tradingItemId=2653595 and dataItemId=112099 and valueDate >= DATEADD(Month,-3,GETDATE()) order by valueDate desc"
fin_returns <- dbGetQuery(conn,query9)

#Financial Factor Data
query11 <- "SELECT [valueDate],[value]
  FROM [Xpressfeed].[dbo].[ciqIndexValue] where tradingItemId=534993233 and dataItemId=112099 and valueDate >= DATEADD(Month,-3,GETDATE()) order by valueDate desc"
cap_returns <- dbGetQuery(conn,query9)

dbDisconnect(conn)
```

```{r}
# value Factor Data
colnames(value_returns)[c(1, 2)] <- c("Date", "closePrice")
value_returns <- value_returns %>%
  arrange(Date) %>%
  mutate(prevPrice = lag(closePrice, 1),
         dailyReturn = (closePrice - prevPrice) / prevPrice)
value_returns <- value_returns[-(1:1),]

#Growth Factor data
colnames(growth_returns)[c(1, 2)] <- c("Date", "closePrice")
growth_returns <- growth_returns %>%
  arrange(Date) %>%
  mutate(prevPrice = lag(closePrice, 1),
         dailyReturn = (closePrice - prevPrice) / prevPrice)
growth_returns <- growth_returns[-(1:1),]

# S&P500 Index Data
colnames(snp_returns)[c(1, 2)] <- c("Date", "closePrice")
snp_returns <- snp_returns %>%
  arrange(Date) %>%
  mutate(prevPrice = lag(closePrice, 1),
         dailyReturn = (closePrice - prevPrice) / prevPrice)
snp_returns <- snp_returns[-(1:1),]

#Dividend Factor Data
colnames(div_returns)[c(1, 2)] <- c("Date", "closePrice")
div_returns <- div_returns %>%
  arrange(Date) %>%
  mutate(prevPrice = lag(closePrice, 1),
         dailyReturn = (closePrice - prevPrice) / prevPrice)
div_returns <- div_returns[-(1:1),]

#Financial Factor Data
colnames(fin_returns)[c(1, 2)] <- c("Date", "closePrice")
fin_returns <- fin_returns %>%
  arrange(Date) %>%
  mutate(prevPrice = lag(closePrice, 1),
         dailyReturn = (closePrice - prevPrice) / prevPrice)
fin_returns <- fin_returns[-(1:1),]

#Quality Factor Data
colnames(cap_returns)[c(1, 2)] <- c("Date", "closePrice")
cap_returns <- cap_returns %>%
  arrange(Date) %>%
  mutate(prevPrice = lag(closePrice, 1),
         dailyReturn = (closePrice - prevPrice) / prevPrice)
cap_returns <- cap_returns[-(1:1),]
```

### Sharpe Ratio Value Strategy

```{r echo=FALSE}
# 1. Calculate Average Return for each stock and then the overall average for top 100 stocks
stock_returns <- stock_returns[,-(1:1)]
avg_stock_returns <- colMeans(stock_returns, na.rm = TRUE)
overall_avg_stock_return <- mean(avg_stock_returns)

avg_value_return <- mean(value_returns$dailyReturn, na.rm = TRUE)

# 2. Benchmark Comparison
avg_snp_return <- mean(snp_returns$dailyReturn, na.rm = TRUE)

# 3. Risk-Adjusted Performance (Sharpe Ratio)
# Assuming a risk-free rate of 0.001 (0.1% monthly, but you can adjust this)
risk_free_rate <- 0.001

sharpe_stocks <- (avg_stock_returns - risk_free_rate) / apply(stock_returns, 2, sd, na.rm = TRUE)
overall_sharpe_stock <- mean(sharpe_stocks)

sharpe_value <- (avg_value_return - risk_free_rate) / sd(value_returns$dailyReturn, na.rm = TRUE)

cat("Sharpe Ratio of Top 50 Value Strategy Stocks:", overall_sharpe_stock, "\n")
cat("Sharpe Ratio of Value Factor:", sharpe_value, "\n")
```
#### Performance Comparison Value Strategy
```{r}
# 5. Visual Representation
cumulative_stocks <- t(apply(stock_returns + 1, 1, cumprod)) - 1
overall_cumulative_stock <- rowMeans(cumulative_stocks)

cumulative_value <- cumprod(1 + value_returns$dailyReturn) - 1
cumulative_snp <- cumprod(1 + snp_returns$dailyReturn) - 1

plot(overall_cumulative_stock, type = "l", col = "blue", ylim = c(min(c(overall_cumulative_stock, cumulative_value, cumulative_snp)), max(c(overall_cumulative_stock, cumulative_value, cumulative_snp))), xlab = "Time", ylab = "Cumulative Return", main = "Performance Comparison")
lines(cumulative_value, col = "red")
lines(cumulative_snp, col = "green")
legend("topright", legend = c("Top 50 Stocks", "Value Factor", "S&P 500"), fill = c("blue", "red", "green"))

# Print results
cat("Average Return of Top 50 Stocks:", overall_avg_stock_return, "\n")
cat("Average Return of Value Factor:", avg_value_return, "\n")
cat("Average Return of S&P 500:", avg_snp_return, "\n")
```

```{r}
portfolio_daily_returns <- rowSums(stock_returns) / 50

# Perform the t-test
t_test <- t.test(portfolio_daily_returns, value_returns$dailyReturn)
cat("T-test Results:", t_test$p.value, "\n")

# Calculate rolling standard deviation (volatility) for a window of, say, 5 days (you can adjust this)
rolling_volatility_portfolio <- rollapply(portfolio_daily_returns, width = 5, FUN = sd, align = "right", fill = NA)
rolling_volatility_value <- rollapply(value_returns$dailyReturn, width = 5, FUN = sd, align = "right", fill = NA)

# Plot the volatilities
plot(rolling_volatility_portfolio, type = "l", col = "blue", 
     ylim = c(min(c(rolling_volatility_portfolio, rolling_volatility_value), na.rm = TRUE), 
         max(c(rolling_volatility_portfolio, rolling_volatility_value), na.rm = TRUE))
,
     xlab = "Time", ylab = "Volatility", main = "Volatility Comparison")
lines(rolling_volatility_value, col = "red")
legend("topright", legend = c("Top 50 Stocks", "Value Factor"), fill = c("blue", "red"))
```

```{r}
combined_returns <- data.frame(
  Top50Stocks = portfolio_daily_returns,
  ValueFactor = value_returns$dailyReturn,
  SNP500 = snp_returns$dailyReturn
)
cor_matrix <- cor(combined_returns, use = "complete.obs")
print(cor_matrix)
# Create the correlation plot
corrplot(cor_matrix, method = "circle")
```






### Sharpe Ratio Growth Strategy

```{r echo=FALSE}
# 1. Calculate Average Return for each stock and then the overall average for top 100 stocks
growth_stock_returns <- growth_stock_returns[,-(1:1)]
avg_growth_stock_returns <- colMeans(growth_stock_returns, na.rm = TRUE)
overall_avg_growth_stock_returns <- mean(avg_growth_stock_returns)



avg_growth_return <- mean(growth_returns$dailyReturn, na.rm = TRUE)

# 3. Risk-Adjusted Performance (Sharpe Ratio)
# Assuming a risk-free rate of 0.001 (0.1% monthly, but you can adjust this)
risk_free_rate <- 0.001

sharpe_growth_stocks <- (avg_growth_stock_returns - risk_free_rate) / apply(growth_stock_returns, 2, sd, na.rm = TRUE)
overall_sharpe_stock <- mean(sharpe_growth_stocks)

sharpe_growth <- (avg_growth_return - risk_free_rate) / sd(growth_returns$dailyReturn, na.rm = TRUE)

cat("Sharpe Ratio of Top 50 Growth Stocks:", overall_sharpe_stock, "\n")
cat("Sharpe Ratio of Growth Factor:", sharpe_growth, "\n")
```


#### Performance Comparison Growth Strategy
```{r}
# 5. Visual Representation
cumulative_growth_stocks <- t(apply(growth_stock_returns + 1, 1, cumprod)) - 1
overall_cumulative_stock <- rowMeans(cumulative_growth_stocks)

cumulative_growth <- cumprod(1 + growth_returns$dailyReturn) - 1

plot(overall_cumulative_stock, type = "l", col = "blue", ylim = c(min(c(overall_cumulative_stock, cumulative_growth, cumulative_snp)), max(c(overall_cumulative_stock, cumulative_growth, cumulative_snp))), xlab = "Time", ylab = "Cumulative Return", main = "Performance Comparison")
lines(cumulative_growth, col = "red")
lines(cumulative_snp, col = "green")
legend("topright", legend = c("Top 50 Growth Stocks", "Growth Factor", "S&P 500"), fill = c("blue", "red", "green"))

# Print results
cat("Average Return of Top 50 Growth Stocks:", overall_avg_growth_stock_returns, "\n")
cat("Average Return of growth Factor:", avg_growth_return, "\n")
cat("Average Return of S&P 500:", avg_snp_return, "\n")
```

### Growth Stocks Rolling Volitality Stocks
```{r}
portfolio_growth_daily_returns <- rowSums(growth_stock_returns) / 50

# Perform the t-test
t_test <- t.test(portfolio_growth_daily_returns, growth_returns$dailyReturn)
cat("T-test Results:", t_test$p.value, "\n")

# Calculate rolling standard deviation (volatility) for a window of, say, 5 days (you can adjust this)
rolling_volatility_portfolio <- rollapply(portfolio_growth_daily_returns, width = 5, FUN = sd, align = "right", fill = NA)
rolling_volatility_growth <- rollapply(growth_returns$dailyReturn, width = 5, FUN = sd, align = "right", fill = NA)

# Plot the volatilities
plot(rolling_volatility_portfolio, type = "l", col = "blue", 
     ylim = c(min(c(rolling_volatility_portfolio, rolling_volatility_growth), na.rm = TRUE), 
         max(c(rolling_volatility_portfolio, rolling_volatility_growth), na.rm = TRUE))
,
     xlab = "Time", ylab = "Volatility", main = "Volatility Comparison")
lines(rolling_volatility_growth, col = "red")
legend("topright", legend = c("Top 50 Growth Stocks", "Growth Factor"), fill = c("blue", "red"))
```

```{r}
combined_returns <- data.frame(
  Top50GrowthStocks = portfolio_growth_daily_returns,
  GrowthFactor = growth_returns$dailyReturn,
  SNP500 = snp_returns$dailyReturn
)

cor_matrix <- cor(combined_returns, use = "complete.obs")
print(cor_matrix)
# Create the correlation plot
corrplot(cor_matrix, method = "circle")
```

### Sharpe Ratio Dividend Strategy

```{r echo=FALSE}
# 1. Calculate Average Return for each stock and then the overall average for top 100 stocks
div_stock_returns <- div_stock_returns[,-(1:1)]
avg_div_stock_returns <- colMeans(div_stock_returns, na.rm = TRUE)
overall_avg_div_stock_returns <- mean(avg_div_stock_returns)



avg_div_return <- mean(div_returns$dailyReturn, na.rm = TRUE)

# 3. Risk-Adjusted Performance (Sharpe Ratio)
# Assuming a risk-free rate of 0.001 (0.1% monthly, but you can adjust this)
risk_free_rate <- 0.001

sharpe_div_stocks <- (avg_div_stock_returns - risk_free_rate) / apply(div_stock_returns, 2, sd, na.rm = TRUE)
overall_sharpe_stock <- mean(sharpe_div_stocks)

sharpe_div <- (avg_div_return - risk_free_rate) / sd(div_returns$dailyReturn, na.rm = TRUE)

cat("Sharpe Ratio of Top 50 Dividend Stocks:", overall_sharpe_stock, "\n")
cat("Sharpe Ratio of Dividend Factor:", sharpe_div, "\n")
```


#### Performance Comparison Growth Strategy
```{r}
# 5. Visual Representation
cumulative_div_stocks <- t(apply(div_stock_returns + 1, 1, cumprod)) - 1
overall_cumulative_stock <- rowMeans(cumulative_div_stocks)

cumulative_div <- cumprod(1 + div_returns$dailyReturn) - 1

plot(overall_cumulative_stock, type = "l", col = "blue", ylim = c(min(c(overall_cumulative_stock, cumulative_div, cumulative_snp)), max(c(overall_cumulative_stock, cumulative_div, cumulative_snp))), xlab = "Time", ylab = "Cumulative Return", main = "Performance Comparison")
lines(cumulative_div, col = "red")
lines(cumulative_snp, col = "green")
legend("topright", legend = c("Top 50 Dividend Stocks", "Dividend Factor", "S&P 500"), fill = c("blue", "red", "green"))

# Print results
cat("Average Return of Top 50 Dividend Stocks:", overall_avg_div_stock_returns, "\n")
cat("Average Return of Dividend Factor:", avg_div_return, "\n")
cat("Average Return of S&P 500:", avg_snp_return, "\n")
```

### Growth Stocks Rolling Volitality Stocks
```{r}
portfolio_div_daily_returns <- rowSums(div_stock_returns) / 50

# Perform the t-test
t_test <- t.test(portfolio_div_daily_returns, div_returns$dailyReturn)
cat("T-test Results:", t_test$p.value, "\n")

# Calculate rolling standard deviation (volatility) for a window of, say, 5 days (you can adjust this)
rolling_volatility_portfolio <- rollapply(portfolio_div_daily_returns, width = 5, FUN = sd, align = "right", fill = NA)
rolling_volatility_div <- rollapply(div_returns$dailyReturn, width = 5, FUN = sd, align = "right", fill = NA)

# Plot the volatilities
plot(rolling_volatility_portfolio, type = "l", col = "blue", 
     ylim = c(min(c(rolling_volatility_portfolio, rolling_volatility_div), na.rm = TRUE), 
         max(c(rolling_volatility_portfolio, rolling_volatility_div), na.rm = TRUE))
,
     xlab = "Time", ylab = "Volatility", main = "Volatility Comparison")
lines(rolling_volatility_div, col = "red")
legend("topright", legend = c("Top 50 Dividend Stocks", "Dividend Factor"), fill = c("blue", "red"))
```

```{r}
combined_returns <- data.frame(
  Top50DivStocks = portfolio_div_daily_returns,
  DivFactor = div_returns$dailyReturn,
  SNP500 = snp_returns$dailyReturn
)

cor_matrix <- cor(combined_returns, use = "complete.obs")
print(cor_matrix)
# Create the correlation plot
corrplot(cor_matrix, method = "circle")
```


### Sharpe Ratio Financial Strategy

```{r echo=FALSE}
# 1. Calculate Average Return for each stock and then the overall average for top 100 stocks
fin_stock_returns <- fin_stock_returns[,-(1:1)]
avg_fin_stock_returns <- colMeans(fin_stock_returns, na.rm = TRUE)
overall_avg_fin_stock_returns <- mean(avg_fin_stock_returns)



avg_fin_return <- mean(fin_returns$dailyReturn, na.rm = TRUE)

# 3. Risk-Adjusted Performance (Sharpe Ratio)
# Assuming a risk-free rate of 0.001 (0.1% monthly, but you can adjust this)
risk_free_rate <- 0.001

sharpe_fin_stocks <- (avg_fin_stock_returns - risk_free_rate) / apply(fin_stock_returns, 2, sd, na.rm = TRUE)
overall_sharpe_stock <- mean(sharpe_fin_stocks)

sharpe_fin <- (avg_fin_return - risk_free_rate) / sd(fin_returns$dailyReturn, na.rm = TRUE)

cat("Sharpe Ratio of Top 50 Financial Stocks:", overall_sharpe_stock, "\n")
cat("Sharpe Ratio of Financial Factor:", sharpe_fin, "\n")
```


#### Performance Comparison Financial Strategy
```{r}
# 5. Visual Representation
cumulative_fin_stocks <- t(apply(fin_stock_returns + 1, 1, cumprod)) - 1
overall_cumulative_stock <- rowMeans(cumulative_fin_stocks)

cumulative_fin <- cumprod(1 + fin_returns$dailyReturn) - 1

plot(overall_cumulative_stock, type = "l", col = "blue", ylim = c(min(c(overall_cumulative_stock, cumulative_fin, cumulative_snp)), max(c(overall_cumulative_stock, cumulative_fin, cumulative_snp))), xlab = "Time", ylab = "Cumulative Return", main = "Performance Comparison")
lines(cumulative_fin, col = "red")
lines(cumulative_snp, col = "green")
legend("topright", legend = c("Top 50 Financial Stocks", "Financial Factor", "S&P 500"), fill = c("blue", "red", "green"))

# Print results
cat("Average Return of Top 50 Financial Stocks:", overall_avg_fin_stock_returns, "\n")
cat("Average Return of Financial Factor:", avg_fin_return, "\n")
cat("Average Return of S&P 500:", avg_snp_return, "\n")
```

### Financials Stocks Rolling Volitality Stocks
```{r}
portfolio_fin_daily_returns <- rowSums(fin_stock_returns) / 50

# Perform the t-test
t_test <- t.test(portfolio_fin_daily_returns, fin_returns$dailyReturn)
cat("T-test Results:", t_test$p.value, "\n")

# Calculate rolling standard deviation (volatility) for a window of, say, 5 days (you can adjust this)
rolling_volatility_portfolio <- rollapply(portfolio_fin_daily_returns, width = 5, FUN = sd, align = "right", fill = NA)
rolling_volatility_fin <- rollapply(fin_returns$dailyReturn, width = 5, FUN = sd, align = "right", fill = NA)

# Plot the volatilities
plot(rolling_volatility_portfolio, type = "l", col = "blue", 
     ylim = c(min(c(rolling_volatility_portfolio, rolling_volatility_fin), na.rm = TRUE), 
         max(c(rolling_volatility_portfolio, rolling_volatility_fin), na.rm = TRUE))
,
     xlab = "Time", ylab = "Volatility", main = "Volatility Comparison")
lines(rolling_volatility_fin, col = "red")
legend("topright", legend = c("Top 50 Financial Stocks", "Financial Factor"), fill = c("blue", "red"))
```

```{r}
combined_returns <- data.frame(
  Top50FinStocks = portfolio_fin_daily_returns,
  FinFactor = fin_returns$dailyReturn,
  SNP500 = snp_returns$dailyReturn
)
cor_matrix <- cor(combined_returns, use = "complete.obs")
print(cor_matrix)
# Create the correlation plot
corrplot(cor_matrix, method = "circle")

```


### Sharpe Ratio capital Creation/Stability Strategy

```{r echo=FALSE}
# 1. Calculate Average Return for each stock and then the overall average for top 100 stocks
cap_stock_returns <- cap_stock_returns[,-(1:1)]
avg_cap_stock_returns <- colMeans(cap_stock_returns, na.rm = TRUE)
overall_avg_cap_stock_returns <- mean(avg_cap_stock_returns)



avg_cap_return <- mean(cap_returns$dailyReturn, na.rm = TRUE)

# 3. Risk-Adjusted Performance (Sharpe Ratio)
# Assuming a risk-free rate of 0.001 (0.1% monthly, but you can adjust this)
risk_free_rate <- 0.001

sharpe_cap_stocks <- (avg_cap_stock_returns - risk_free_rate) / apply(cap_stock_returns, 2, sd, na.rm = TRUE)
overall_sharpe_stock <- mean(sharpe_cap_stocks)

sharpe_cap <- (avg_cap_return - risk_free_rate) / sd(cap_returns$dailyReturn, na.rm = TRUE)

cat("Sharpe Ratio of Top 50 Quality Stocks:", overall_sharpe_stock, "\n")
cat("Sharpe Ratio of Financial Factor:", sharpe_cap, "\n")
```


#### Performance Comparison Capital Creation/Stabilty Strategy
```{r}
# 5. Visual Representation
cumulative_cap_stocks <- t(apply(cap_stock_returns + 1, 1, cumprod)) - 1
overall_cumulative_stock <- rowMeans(cumulative_cap_stocks)

cumulative_cap <- cumprod(1 + cap_returns$dailyReturn) - 1

plot(overall_cumulative_stock, type = "l", col = "blue", ylim = c(min(c(overall_cumulative_stock, cumulative_cap, cumulative_snp)), max(c(overall_cumulative_stock, cumulative_cap, cumulative_snp))), xlab = "Time", ylab = "Cumulative Return", main = "Performance Comparison")
lines(cumulative_cap, col = "red")
lines(cumulative_snp, col = "green")
legend("topright", legend = c("Top 50 Stabilty Stocks", "Quality Factor", "S&P 500"), fill = c("blue", "red", "green"))

# Print results
cat("Average Return of Top 50 Stability Stocks:", overall_avg_cap_stock_returns, "\n")
cat("Average Return of Quality Factor:", avg_cap_return, "\n")
cat("Average Return of S&P 500:", avg_snp_return, "\n")
```

### Quality Stocks Rolling Volitality Stocks
```{r}
portfolio_cap_daily_returns <- rowSums(cap_stock_returns) / 50

# Perform the t-test
t_test <- t.test(portfolio_cap_daily_returns, cap_returns$dailyReturn)
cat("T-test Results:", t_test$p.value, "\n")

# Calculate rolling standard deviation (volatility) for a window of, say, 5 days (you can adjust this)
rolling_volatility_portfolio <- rollapply(portfolio_cap_daily_returns, width = 5, FUN = sd, align = "right", fill = NA)
rolling_volatility_cap <- rollapply(cap_returns$dailyReturn, width = 5, FUN = sd, align = "right", fill = NA)

# Plot the volatilities
plot(rolling_volatility_portfolio, type = "l", col = "blue", 
     ylim = c(min(c(rolling_volatility_portfolio, rolling_volatility_cap), na.rm = TRUE), 
         max(c(rolling_volatility_portfolio, rolling_volatility_cap), na.rm = TRUE))
,
     xlab = "Time", ylab = "Volatility", main = "Volatility Comparison")
lines(rolling_volatility_cap, col = "red")
legend("topright", legend = c("Top 50 Stability Stocks", "Quality Factor"), fill = c("blue", "red"))
```

```{r}
combined_returns <- data.frame(
  Top50QualityStocks = portfolio_cap_daily_returns,
  QualityFactor = cap_returns$dailyReturn,
  SNP500 = snp_returns$dailyReturn
)
cor_matrix <- cor(combined_returns, use = "complete.obs")
print(cor_matrix)
# Create the correlation plot
corrplot(cor_matrix, method = "circle")
```
